---
title: "HW 1"
author: "Matthew Fein"
date: "January 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Machine Learning HW #1 

3.6.1
Data was obtained from http://users.stat.ufl.edu/~winner/datasets.html.
The dataset includes pricing and various other attributes for 153 hybrid-electric cars.

```{r data}
data <- read.csv("hybrid_reg.csv", header = TRUE)
data1 <- read.csv("hybrid_reg.csv", header = TRUE)
library(MASS)
library(ISLR)

```

3.6.2
Acceleration rate is the predictor variable and msrp is the predictee.
```{r simple regression}

names(data)
attach(data)

lm.fit <- lm(msrp~accelrate)

lm.fit
summary(lm.fit)

names(lm.fit)
coef(lm.fit)

confint(lm.fit)


predict(lm.fit,data.frame(accelrate=(c(8,10,12))), interval="confidence")
predict(lm.fit,data.frame(accelrate=(c(8,10,12))), interval="prediction")


plot(accelrate,msrp)
abline(lm.fit)
abline(lm.fit,lwd=3)
abline(lm.fit,lwd=3,col="red")
plot(accelrate,msrp,col="red")
plot(accelrate,msrp,pch=20)
plot(accelrate,msrp,pch="+")
plot(1:20,1:20,pch=1:20)
par(mfrow=c(2,2))
plot(lm.fit)
plot(predict(lm.fit), residuals(lm.fit))
plot(predict(lm.fit), rstudent(lm.fit))
plot(hatvalues(lm.fit))
which.max(hatvalues(lm.fit))

```

3.6.3
MSRP is being predicted by acceleration rate and mpgmpe (a measure of mpg when fully charged).  Data was trimmed to eliminate collinearity effects which made "vif" trigger an error.
```{r}
data <- data[ , -2]
data <- data[ ,-8]
lm.fit=lm(msrp~accelrate+mpgmpge,data=data)
summary(lm.fit)
lm.fit=lm(msrp~.,data=data)
summary(lm.fit)
library(car)
vif(lm.fit)
lm.fit1=lm(msrp~accelrate+mpg)
summary(lm.fit1)

```

3.6.4
Interaction term is  added to previous model.
```{r}
summary(lm(msrp~accelrate*mpg))
```

3.6.5

```{r}
lm.fit2=lm(msrp~mpg+I(mpg^2))
summary(lm.fit2)
lm.fit=lm(msrp~mpg)
anova(lm.fit,lm.fit2)
par(mfrow=c(2,2))
plot(lm.fit2)
lm.fit5=lm(msrp~poly(mpg,5))
summary(lm.fit5)
summary(lm(msrp~log(mpg)))
```

3.6.6
The variables car class and year are used to predict msrp.
```{r}
lm.fit=lm(msrp~carclass*year, data = data1)
summary(lm.fit)

contrasts(carclass)
```

3.6.7

```{r}
LoadLibraries=function(){
 library(ISLR)
 library(MASS)
 print("The libraries have been loaded.")
 }
LoadLibraries
LoadLibraries()
```

